\section{Introduction}

%This sentence has an example citation~\cite{DBLP:journals/infsof/BinkleyMI22} 
Our team was approached by our client, Dr. Ho, to create a web application for a casino. The app focused on Blackjack. According to the needs of our client, we allowed for there to be guest, account, and admin users. We also needed to have a tutorial for blackjack that new users could view, which was found on the landing page. We created a lobby, which is where a user would be directed to upon login. Every new user received \$2500 worth of chips, and whenever a user got to \$0, they would be replenished to \$2500 again. For all users, the lobby had the existing tables and presented the option to the user to create a table. The user that created the table would set the minimum bet, the payout ratio, and the maximum amount of players at the table (the minimum was determined to be 1 player, in addition to the dealer). This table information was displayed in the lobby. If a user were in a game (which was within a table), they could leave whenever they want, but if they left in the middle of the game, they would lose their bet. Users could also change their ace values between 1 or 11 whenever they wanted, but if they had more than one ace, all of them had to be the same value. The table disappeared from the lobby when no players remained in it. \\

\noindent Account users and admin had access to their personal game statistics, had the ability to add friends, and had the ability to view their friend list. Admin had the addional ablity to manage all users' account information, such as username, email, and password. Chats were created, with one type of chat having been for within a table, and the other type of chat was in the lobby. This second type of chat was either used for chatting with friends or admin. When a user wanted to change account information, they would have sent a chat to an admin account, so that the admin could change it. \\

\noindent The remaining requirements we accomplished were for the UI. The game needed to be colorful, with red as the color theme. Lastly, we needed a logo, which was used on our landing page and as our home page navigator.

