\subsection{Non-Functional Requirements}

\subsubsection{Category: User Interface}

\textbf{ID: Red theme}
\begin{enumerate}
    \item Description: The web app should be colorful, aesthetically pleasing, and have a consistent red theme throughout its GUI.
    \item Affects: S1 (Login), S3 (Create Account), S4 (View Friends List), S9 (View Table Info), S19 (View Game History), S21 (View Tutorial)
\end{enumerate}

\smallskip

\textbf{ID: Logo displayed throughout app}
\begin{enumerate}
    \item Description: The company's logo should be visible throughout the app across its multiple pages.
    \item Affects: S1 (Login), S3 (Create Account), S4 (View Friends List), S9 (View Table Info), S19 (View Game History), S21 (View Tutorial)
\end{enumerate}

\smallskip

\textbf{ID: Include animations}
\begin{enumerate}
    \item Description: Include moving parts and animations for visual engagement.
    \item Affects: S26 (Play Blackjack)
\end{enumerate}

\subsubsection{Category: Security}

\textbf{ID: Enforce password policies upon creation}
\begin{enumerate}
    \item Description: Only allow the creation of an account if the user's proposed password is at least 8 characters long.
    \item Affects: S3 (Create Account)
\end{enumerate}

\smallskip

\textbf{ID: Encrypt passwords}
\begin{enumerate}
    \item Description: Encrypt the passwords of all users' accounts.
    \item Affects: S1 (Login), S3 (Create Account)
\end{enumerate}

\subsubsection{Category: Performance}

\textbf{ID: 1 minute maximum loading time}
\begin{enumerate}
    \item Description: The app's loading time should not affect the user's experience. Keep loading time under a minute.
    \item Affects: All user stories
\end{enumerate}

\smallskip

\textbf{ID: Optimize Ace Value}
\begin{enumerate}
    \item Description: The game auto-optimizes an ace value to prevent busts.
    \item Affects: S15 (Change Ace Value)
\end{enumerate}

%\subsubsection{add other subsections as needed, or delete irrelevant subsections}
